### 2015-03-02 fundamentals/impl.tex
addresses the concern that the ABM section intro was confusing. The comment from Erich was "Im still struggling with how to open this section. What is meant by the natural perspective"
addresses the comment from Erich 'what is the advantage of this?  Maybe the point is that these two agents can each be given different sets of rules governing how they will interact with the simulation.  Assumedly they're acting in their own best interest according to a simple, rational set of rules... but that's really up to the archetype modeler :)'

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} provides a natural
perspective from which to model a given problem. In the nuclear fuel cycle
context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

>>>>

\Cyclus implements an \acrlong{ABM} paradigm. \gls{ABM} enables model
development to take place at an agent level rather than a system level. In the
nuclear fuel cycle context, for example, an analyst can design a reactor agent
that is entirely independent from a fuel fabrication agent. Defining the
behavior of both agents according to the
\gls{API} contract is sufficient for them to interact with one another as
bona fide actors in the simulation.  The two archetype libraries can be used in
the same simulation without any shared knowledge, allowing modelers to
construct a simulation from building blocks of many types and origins.
